Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-01-18 draft.tex
additions to multiple sections

>>>>

		The explanations using the previously described surrogate model are generated with Local
		Interpretable Model-agnostic Explanations (LIME). This section will describe in detail how
		individual explanations are generated at a local level for individual samples, as well as
		how the usefulness of the explanations can be evaluated in general.
			\subsubsection{Generation of the Explanations}
			Because of the multi-shaped nature and independence of the input layers of the model,
			the explanations cannot be generated directly from the input itself. However, because
			the sub-models are separate from one another, having no influence on each other before
			being concatenated at the terminus, only the terminus part of the model is relevant
			for assessing the importance of the features in a single evaluation. This does,
			however, present two challenges:
				\item There are multiple input rows per sample.
				\item The features cannot be used directly for assessment at the terminus input
					layer.
			The first problem can be solved by taking the mean of the explanation weights of each
			feature produced by each row of the sample features. This results in an average
			contribution of each feature to the classification of the model. Because the
			end-classification of the surrogate is also a mean, the means of the LIME-results are
			an accurate representation of the aggregate influence.
			I approached the second problem by generating intermediate data for the
			LIME-evaluation. Intermediate data was generated by first decomposing the surrogate
			model into its component models, the sub-models and the terminus, and for each
			sub-model, running a prediction on the given input features. The results of the
			predictions of the sub-models were stored and used for further analysis. This was done
			not only for the sample explanation data but also for the training data, to use as an
			input for the LIME explainer.
			\subsubsection{Evaluation of the Explanations}
